---
title: "Homework 1"
author: Adarsh Ramakrishnan
output: github_document
---

This is my homework 1 solution:


Loading tidyverse library:

```{r libraries}
library(tidyverse)
library(readxl)
```


## Problem 1

Read the trash wheel collection dataset

```{r}
trashwheel_df = read_xlsx("./data/trash_wheel_collection.xlsx", 
  sheet = "Mr. Trash Wheel",
  range = cell_cols("A:N")) %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(
    sports_balls = round(sports_balls), 
    sports_balls = as.integer(sports_balls)
  )
```


Read the precipitation dataset

```{r}
precip_df_2018 = read_xlsx("./data/trash_wheel_collection.xlsx", 
  sheet = "2018 Precipitation",
  skip = 1)%>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2018) %>%
  relocate(year)

precip_df_2017 = read_xlsx("./data/trash_wheel_collection.xlsx", 
  sheet = "2017 Precipitation",
  skip = 1)%>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2017) %>%
  relocate(year)
```

Combine annual precipitation

```{r}
month_df = tibble(month = 1:12, month_name = month.name)
precip_df = bind_rows(precip_df_2018,precip_df_2017) 
left_join(precip_df, month_df, by = "month")





```

The dataset contains information from the Mr.Trashwheel trash collector in Baltimore. As trash enters the inner harbor, the trashwheel collects trash and stores it in a dumpster. The dataset contains information on year, month, and trash collected, include some specific kinds of trash. There are a total of `r nrow(trashwheel_df)`  rows in our final dataset. Additional data sheets include month precipitation data

